 
Has the act of raping other humans become monotonous, and the effort of leaving 
your home become too much? If so, this chapter is definitely worth looking into. 
Followed correctly, this simple manual will show you different methods of rape 
that can be a safe and fun alternative to raping women or children, and it will 
show how such acts can be productive and informative. Written by the 
critically-acclaimed author James B. Rustles, this short manual contains several 
surefire methods to feeding your desire to rape, while staying in the legal 
realms of the law.


\section*{Solution 1: SELF-RAPE}

While some may doubt this alternative to rape, it has been proven that self-rape 
is a great way to curb your appetite for rape, and can result in an amazing 
self-bonding experience with ones body only achievable by means of self-rape.

1) Treat yourself to a few drinks or other soft drugs that are available or near 
your location; loosen up a bit and relax a little. Turn on the TV, radio, or 
just lie down on the couch. Make sure you get in a comfortable and relaxed 
state.

2) If things are already going well and you’re feeling about to pass out, 
continue, but if not, you may need some extra help. In this case throw half a 
roofie tablet into the drink when you’re not looking, and then continue to drink 
at a comfortable pace.

3) From here it's incredibly easy to take advantage of your unsuspecting self. 
Simply take off your pants (by force if necessary).

4) Slide your hand onto your penis. It should be erect by now. Stroke your penis 
slowly, but firmly and increase the pace as you go. Slide a couple fingers into 
your asshole, sodomy is historically a key part in self-rape and is still 
relevant today. (Note: it may hurt momentarily, but you will experience pleasure 
after your asshole gets accustomed to it.)

5) You’ll know when you have been successful if a milky white liquid erupts from 
the tip. This liquid is called semen. As appetizing as this liquid may seem, it 
is not recommended you ingest it, however there are no health risks involved in 
doing so.


Other various methods of self-rape include but are not limited to:


    Leaving a plunger in the toilet and sitting on it when you go to use the 
restroom (A.K.A. The Hellen Keller). (This method may result in death or serious 
colon injury.)


    Sticking a suction cup phallus shaped object on a chair and leaving it there 
until you sit on it (this method is known to be slightly uncomfortable, however 
is still a healthy and widely used method).


    Obtaining a life-size poster of your naked backside with an appropriately 
positioned anal cavity can simulate self-rape to a certain degree.


    Placing a vacuum cleaner hose around your erect penis.  From here simply 
turning on the aforementioned vacuum can produce rape-like sensations.



\section*{Solution 2: RAPING INANIMATE OBJECTS}

Raping inanimate objects result with no legal repercussions and no life changing 
consequences. In Afghanistan, it's very common to make love to sand dunes before 
you make love to a woman. It is also common for young boys to make insertions 
into their bed to insert their penis into the tight hole of the fabric. Some 
inanimate objects


Steps to a common method of the rape of inanimate objects:


1) Open a door until there is a certain amount of room to diligently put your 
penis in the remaining space. this will give pleasure as it simulates sexual 
activity to the shaft and tip of the penis.