 
In nature, we are presented with a wonderful plethora of sexual exploits, from 
the smooth and muscular contractions of a dolphin to the rough and powerful 
penetration of a stallion. So if it should ever come to pass that you become 
bored of having all the natural coitus you could ask for, you could begin 
engaging in natural coitus with animals. The great thing here is that there are 
many species of animals from which to choose from and, the structure of the 
genitalia in animals varies from species to species, meaning there is more than 
enough variety. For example, a dog’s vagina is incredibly tight and soft, while 
a dolphin’s is smoother and more muscular. You can begin your natural coitus 
endeavor by experimenting with a neighbor’s dog or cat. Be very wary of felines 
however, their genitals are very small and tight which will cause them to lash 
out when you first try to initiate the encounter. Be aware that felines have 
very sharp claws and may attempt to maim your genitals. The best way to prevent 
this scenario and make the experience as a whole more enjoyable would be to tape 
their front paws together, in a comfortable position, and have them tied up to a 
secure object, which would refrain them from running or escaping. This way you 
may position them to your liking and begin your encounter with the already 
established dominance.

Unfortunately, due to all the benefits of coitus with animals there is a 
downfall. Engaging in coitus with animals has given rise to new diseases, for 
example syphilis, and this being the case it is important to remind the general 
public to wear protection when engaging in coitus with animals, stray or 
domestic.

\section*{Steps to having Natural Coitus with Animals}

\section*{Initiation}

The animal kingdom truly does present a wide array of possible pursuits but it 
is important not to be overwhelmed. Good starters are small domesticated animals 
such as dogs or cats, preferably strays that have not yet had much experience 
with humans intimately, although they may be a bit more rebellious, they are 
their own reward. With moderate amounts of duct tape and a few generous “love 
taps” to show the animal who is the alpha male, you can quickly share the gift 
of natural coitus with your canine companion. Just be sure to silence any would 
be “mating calls” during penetration and bring plenty of absorbent/ soundproof 
materials.

Of course, there are people who might wrongly look down upon one for engaging in 
such a practice, even going so far as to call it forced coitus. This statement 
is ridiculous. To be forced (if one can even ever be actually forced) you must 
first possess a soul, something all animals lack. They can feel joy and sexual 
pleasure, so, as a good pet owner, it is important you reach out to these needs 
and satisfy all the pets in that area.

\section*{Finding an Animal}

       

    Acquiring an animal for which to experiment with is never a problem, 
depending on your location and thanks to the lack of people neutering their 
pets. If you are located in a town or city simply leave out a trap, bought or 
made, with filled with cat food, and be sure to check on this trap daily, be 
careful when checking you never know what you will find but, remember you are  
only keeping the animal if it is a feline or canine. Another option for the city 
dweller is adopt a rescue from your local animal shelter but, be sure to give 
your rescue a bath and a day’s rest before commencing any attempt at natural 
coitus.

           If you are located in a rural area of the country side, then chances 
are that you own or live close by to farm that houses livestock animals, 
including but not limited to: sheep, cattle, horse, or poultry. This situation 
is simple to use to your advantage because, you already spend all day with or 
near the animals. This makes it much easier for you by giving you the ability to 
simply pre-meditate your plan of action days before, allowing you to sneak your 
supplies over to where the natural coitus will occur, wait till the dead of 
night, and sneak over to your location and execute said plan. There is no 
running around for you; all it takes is time and curiosity.

   \section*{Initiating Natural Coitus}

An important factor is to make sure that the animal’s organ is big enough for 
you to work with. It is just as important to choose an animal that is 
appropriate for your height, for example, it would be better for a 6 foot man to 
have coitus with a cow or horse rather than with a feline. In the end, however, 
it will ultimately come down to working with what is available. Many animals can 
be coerced into intercourse by the allure of treats.

The thing to remember about animals is that they are prone to having human like 
characteristics; they have to be relaxed, excited and get worked up just like 
humans in order to not resist and participate. It is essential to keep in mind 
that animals can be dangerous and aggressive. They can, and will most likely, 
rebel against your wish if they are not restrained. Always have a leash at your 
disposal and tie up your animal of choice up before initiating any attempt at 
coitus. With such a short temper on animals, it is purposeful that you know the 
characteristics of the animal you have at your disposal, if attempting coitus 
with a livestock animal, remember they participate in coitus standing. So, if 
the animal is standing, then leave it standing. Do not attempt to lay it down, 
this will only aggravate it. You will next apply the following details to your 
situation; get on your knees and gently grasp its ankles. Use your fingers to 
relax the animal; rub the animal’s body, work the whole body. This procedure 
should continue until the animal begins to “show” that it is ready. To know that 
the animal is ready check and feel for the following signs: its hips begin to 
feel relaxed, the animals overall mood should be in a calm state, it should not 
be exhibiting any signs of aggressiveness, its pants will begin to grow heavier, 
and the animal should soon begin to “show.” Always remember that treats can and 
should be used, but sparingly, to coerce and relax the animal, easing it into 
engaging in the coitus. When it is evident that the animal is ready, this is 
where the protection comes into play. Fix your protection (i.e. a condom) into 
place, making sure it is secure and proceed to next phase.

          

       

    \section*{Consummating the Coitus}

              Again, it is important to adjust the basics that have been 
outlined to your situation. Slowly position yourself, however you feel it best 
but, be careful, you don’t want to destroy the mood she's in. Animals can, at 
times, tend to be very sporadic, again make sure they are tied up only giving 
them so much lee-way. Next, you will want to guide the animal to do your 
bidding, not only will you lead it to water but you will make it drink. Treats, 
can again be used here to get it to where you want it to go.

               Once you have successfully entered the animal it is important to 
hold you position, no matter how much the animal may squirm. Animals cannot call 
for help when properly restrained, therefore one can feel free to use any 
techniques necessary to prove to an animal that you are dominant. You want them 
to get used to it, you want them to know you are man and you control what will 
happen to it. Now slowly grind your pelvis, this is the secret that had made our 
species evolve from cavemen, do not disappoint. Things may begin to get heavy 
but pace is important here, you need to work out a steady pace. Do not be 
selfish, it will be an experience for the both of you. Do whatever you can to 
let the animal enjoy it as well, reward good actions, punish any revolts. Do not 
let it forget that you are in charge. From here the rest of the experience is 
self explanatory.

\section*{Things to consider when planning to engage in intercourse with an animal:}
\begin{itemize}
\item Make sure you are in a secluded area or if in residential area make sure you 
have all blinds heavily closed, tape the animals mouth shut and have soundproof 
material surrounding you when making love to an animal.

\item Be sure to silence the animal’s cries of pleasure when performing natural 
coitus. A passerby or neighbor may hear you.

\item Smaller animals may require a certain amount of lube to be penetrated, being 
as they have naturally smaller orifices.

\item Make sure the animal has been bathed, or more importantly that the area you 
are interested in has been bathed.

\item Protection will save both you and the human race.

\item Penetration points are interchangeable.
\end{itemize}
           \section*{Necro-beastiality and you}

           Necro-beastiality can be very dangerous for its patron. They are 
sticking a piece of themselves into nothing more than a pile of dead and 
decomposing flesh. There is a lot more bacteria at work here, decomposing the 
body than before, raising the stakes of your experiment with animal coitus 
greatly. It is because of this that it is important to know your limitations 
with this particular area of natural coitus. You must know that protection and 
isolation is necessary here, the animal will be secreting fluid and the smell 
will be beyond appalling, the use of a gas mask is advised.

    Although everything is much more passive in this case, and the animals may 
be positioned in whatever  pose, there are key downfalls. In this case 
penetration points are not interchangeable. The animal is cold and hard so are 
its insides. The intestines are cold, hard and will stick to you if they come in 
contact, wrapping themselves around you, even when coming out. A sheet is 
advised to catch all secreting fluid.

   

    When you have completed the coitus, it is essential to dispose of the body. 
Be sure that when looking for a sheet that it is big enough to wrap the animal 
with it, disposing of the body correctly, yet lucratively. You must give thanks 
for the gift it has bestowed upon you. 