 



In human evolution, many civilizations have taken up the use of slaves (the 
existence of slaves has taken place all around the world as well, in America, 
during the 19th century and in Brazil, during the 16th century) which has 
created a cognitive function in the human psyche to sometimes side with their 
captor. This is widely known as Stockholm syndrome. Initially, the subject shows 
extremely aggressive behavior, but gradually, the aggression diminishes as the 
subject realises its escape is impossible. It must side with its captor in order 
to minimize the chances of getting killed.


The process happens very gradually, but it can be accelerated. Techniques often 
used by torturers in war are designed to break the prisoner quicker than time 
alone would. Such techniques are not limited to physical pain, but rather 
emotional and psychological abuse. Examples include having the subjects head 
shaved to rob her\\him of their identity, giving it derogatory nicknames such as 
“dog,” “bitch,” and “slave” to diminish their self-worth. A very common 
technique is to put them on a leash and force them to crawl as if they were an 
animal.


By feeding them and taking care of them over time, they will realize that their 
survival depends on you, and you can shape their mentality by reinforcing good 
behavior and punishing bad behavior. If you punish the subject whenever it shows 
sign of resistance or lack of cooperation, it will slowly learn to obey you. 
Likewise, you can reward good behavior by giving it food when it behaves well 
and allow it to sleep or have a treat when it shows signs of obedience and 
loyalty.


Sleep deprivation is a very effective way of mentally abusing someone and has 
massive impacts on a subject's psyche. Keeping a subject awake for extended 
periods of time can be difficult on your own, but is not impossible with the use 
of uncomfortable tied positions, white noise, loud music and cold water.


The environment in which a subject is kept in heavily influences its level of 
discomfort and mood. Having your subject tied/caged in a basement is more 
effective than having it caged in a luxury bedroom. Also, keep in mind that 
creating a dark and depressive atmosphere in a room can greatly impact the 
subject’s sense of security and comfort. Your subject should only feel safe when 
it is in your arms.


It is recommended that you keep your subject locked up until it has shown 
loyalty and unconditional love. Even after this stage you must maintain strict 
discipline, constantly reminding the subject that you are its Master. Always 
punish bad behavior and reward love and obedience even well after the subject 
has grown accustomed to you.
