

\chapter*{Introduction}
%Quote example
\epigraph{The best relationship I had in my life was a friend turned boyfriend. 
I smiled at him in his birthday party and we slept next to each other on the 
floor. All of a sudden he got on top of me, forced my hands against the floor 
and kissed me. That was one of the most amazing feels in my life, to have a man 
show his confidence and assert his dominance on me physically. It's a 
terrifying 
thought that the boys of today, when they grow up, will be too afraid to act 
like men when true masculinity comes to be socially unacceptable. I'm glad I'm 
from a generation and live in an era where there's still decent men for whom 
strength, prowess and dominance are admirable qualities, incorporable to the 
concept of the gentleman.}{Anonymous.}


\input{chapters/intro}


%\chapter{Defining ``Natural Coitus"}

%\input{chapters/defining_natural_coitus}

\chapter{Natural Coitus and History}

\epigraph{A maiden aged three years and a day may be acquired in marriage by 
coition, and if her deceased husband’s brother cohabited with her she becomes 
his.}{Sanh. 69a, 69b, discussed in Yeb. 60b}

\input{chapters/history}

\chapter{The Psychology and Ethics of Natural Coitus}

\epigraph{There is a reason for men having the superior sex drive over women, 
and the 
greater strength to take it. Evolution has favored man over woman, and given 
him 
the choice of when to reproduce. We have social misgivings about natural sex, 
and have to resort to violent sounding words like "rape" and "molest", when 
humans are the only species that are able to give consent. Consent is merely a 
social construct born out of ancient religions. No other species has ever given 
consent.}{Richard Dawkins}

\input{chapters/psychology_and_ethics}

\chapter{Discrimination against Natural Coitus}
\input{chapters/discrimination_against_natural_coitus}


\chapter{Relationships}

\epigraph{Bitches be on this dick like bees on honey. And by bitches I mean 
nine 
year old girls. And by dick I mean forceful sex.}{Mohammed}

\input{chapters/rapelationships}

\chapter{Finding a Partner}
\input{chapters/finding_a_partner}


%\chapter{Choosing a Partner}
%\input{chapters/choosing_a_partner}


\chapter{Equipment and Tools}
\input{chapters/equipment_and_tools}


\chapter{Breaking Your Partner into Submission}
\epigraph{You need to make them believe that they need their master, that their master 
gives them purpose. Make them believe that to satisfy the master is the purpose 
of their existence.}{Anonymous}
\input{chapters/breaking_your_partner}

\chapter{Evidence Management}
\input{chapters/evidence_management}

\chapter{Animal Coitus}
\input{chapters/animal_coitus}

\chapter{Time to Strike}
\input{chapters/time_to_strike}

\chapter{Evading}
\input{chapters/evading}

\chapter{Social Attitudes Towards Natural Coitus}
\input{chapters/social_attitudes_towards_natural_coitus}

\chapter{Overcoming Opposition: The Unenlightened}
\input{chapters/overcoming_opposition_the_unenlightened}


\chapter{Safe Alternatives}
\input{chapters/alternatives}


\chapter{Hints, Tips, Extras}
\input{chapters/hints_tips_extras}