 
In the increasingly politically correct world we live in today, many people 
might see practices such as, “forceful sex” or “black-face scat fights” as 
offensive or even immoral, especially within the lesbian dominated catholic 
community. This reaction is understandable. Most people do not have to bear the 
cross of an “obscure fetish.” Most people do not have to spend hours sprawling 
through the back alley of the internet for that last beautiful, horrible hit. 
Most people don’t have to live knowing that if a loved one saw they’re internet 
history they would probably be arrested. Most people don’t have to carry a 
cyanide pill with them at all times to prevent their hard drive coming into 
contact with the government. But I say that democracy should not be about “most 
people.”


We “perverts,” we “deviants,” we “serial sex offenders” are the accused 
minority. We stand against intolerable discrimination, not dissimilar to the 
situation faced by many other demographics in the past. The blacks in early 
America too suffered this fate and it is with a deep regret that America 
remembers the untold horrors they gave them. Martin Luther King Jr. died so that 
all men might be equal, whether they like to watch greased up adults in diapers 
eating leftover garlic notwithstanding. Are we really so horrible to allow 
ourselves to act out our urges? Is a dog truly depraved if it follows its 
natural instinct? Why then is it seen as so immoral for a grown man to touch 
himself in a playground? Why am I labelled a “paedophile” for being sexually 
attracted to my ex-wife’s extraordinarily attractive nine year old niece? I’ll 
tell you why, It’s the media’s obsession with boxing every topic into nice 
little borders. It’s the politics of normalising every obscure thought and 
fetish and neatly dusting every abnormality under the carpet. We are not dirt. 
We are people. People who like to forcibly have sex in a natural manner with 
other people or animals.


As you are reading this book, I ask of you (as the probability dictates that you 
are one of “most people”) not to judge me or my beliefs. I ask only that you 
accept me for who I truly am in all my shameful lust. I ask that you do not 
discriminate against me for the views that I uphold as natural. I ask that you 
follow the path of the minority and celebrate the idea of the individual.


Finer points of morality: Is it wrong to commit to a life of natural coitus?


In the eyes of today, the answer appears clear. In today’s society, of course 
the act of natural coitus is deemed “wrong” or “taboo”, but is that your 
response or an ingrained one? Was it considered wrong thousands of years ago 
when noble cavemen took the women they wanted for the higher purpose of 
procreation? In the eyes of a child, coitus holds no more evil than any other 
loving act as they have not yet been indoctrinated into mainstream media. 
Children are naturally curious about sex and act on it without hesitation in 
games of play such as “Doctor” or “Find the Sausage”. It can argued that 
performing natural coitus is an act of love. To give your seed to someone is a 
tremendous gift and one that carries over through a generation. This gift is a 
powerful biological bounty that allows a woman to bear nature’s greatest 
provision. Many a single lady despairs over the barren state of her wombs. What 
natural coitus does, is it gives and let others receive, most usually on all 
fours and crying deeply. It could then be said that playing the “victim” during 
the act of natural coitus is a form of selfishness. If the alpha male performing 
this act enjoys himself and no lasting harm is done to you, then why not allow 
others to enjoy themselves? We have been brainwashed by the news into thinking 
that forcing yourself on someone physically is an act of evil when really it is 
a reaction to basic and natural carnal desires. The act of natural coitus is 
simply the most pure form of this lusting and as a result, the most natural. 
There is nothing wrong in the natural, as this remains as God’s domain.


“For the invisible things of him from the creation of the world are clearly 
seen, being understood by the things that are made, even his eternal power and 
Godhead; so that they are without excuse.” -Romans 1:20


Natural Coitus is an instinctive response to an instinctive situation. When 
faced with a desirable mate out of another’s reach, the default action is to 
take it by force. If it was so abhorrent, then why would it occur across the 
natural spectrum? Guided intercourse is the most sacred act of all, it is pure 
baseless procreation and its power beats at the heart of every animal. To deny a 
man the right to perform natural coitus is to deny a man his very essence.


The popularity of the novel “50 Shades of Grey” confirms much of what we know 
about the female gender. They might say they want equal rights, but deep down 
they only want to be dominated. Ever since the domestication of the human male, 
fetishes such as BDSM have become very popular in western culture. The Irish 
Newspaper, the Star, reveals that 72\% of people enjoy fetish sex. It is safe to 
conclude that most women secretly enjoy performing natural coitus.  