“Victory lies in preparation” has been the motto of many a general. The same 
goes for the man on a solo mission, the lone wolf taking his share of the herd. 
There are many things to consider when going to battle, and for the sake of the 
metaphor, let's see the act of applied lovemaking as a battle. Before you choose 
your battlefield and your timing, which are both of essence, you must make sure 
that you have the proper equipment for your mission. You will need to protect 
yourself, you will need means of attack, transportation, and if your mission 
requires it, a place to hold your prize.


In ancient times it was simpler. A warrior would come, kill the local men, and 
carry the women off. No one would look twice, and it was perfectly acceptable. 
Those times have passed. Subtlety is paramount if you are to be successful. And 
the first subtlety, a very important one, is often easily forgotten. STD's are 
rampant nowadays. From relatively innocent ones like herpes to HIV, you are 
likely to meet at least one of them along the way. So safety first, and bring a 
condom. Not only to protect yourself, but also to protect your partner and, if 
push comes to shove, in order to leave as little DNA as possible. Only if you 
are certain that you your partner is uninfected, will not get pregnant, and you 
have another method of removing DNA, you could do away with condoms, but it is 
still ill advised. Also, in order to protect yourself, you will need clothing 
that prevent your partner from effectively scratching or biting you. These are 
things women tend to do when forcibly resisting, and they both could leave you 
with marks or could scatter your DNA all over your battlefield. Leather and 
denim are good materials to wear on the upper body, and some facial protection 
like a mask or a bandana are no luxuries. As for leg and footwear, you must be 
able to move quickly and agile. You are not making a fashion statement, so cargo 
pants or sweat pants are ideal. Colours should be limited to grey, brown, dark 
blue, dark green and dark red, for these are colours that blend easily in the 
dark but seldom arouse suspicion in daylight. Black is often perceived as 
aggressive, and contrary to popular belief, does not blend in with the night. 
Bright colours draw attention towards you and make it difficult to hide.


As for your means of attack, it is important that you use a weapon you are 
familiar with, that is easily concealed, and that instills fear. You are not out 
to kill or maim, the idea of your weapon is to incapacitate or threaten. If you 
want your partner to be unconscious, do not bother with chloroform. It is a 
myth, she will get nauseous but she will not faint. Also, if you have no prior


experience, blows to the head with blunt objects are ill advised. Too hard and 
she/he will die, too soft and she/he will raise alarm. The best way to do this 
is to spike a drink. Many drugs will do the trick, but safest and easiest to get 
is GHB. Most other drugs will either kill her or land her in a hospital(in 
combination with alcohol), or just won't have the desired effect. But still, if 
you are able to spike her drink, it is not certain that you will be the one to 
reap the benefits. It is quite a task to follow her around, corner her, isolate 
her, and carry her to where you planned. Easier is fear. You can probably scare 
her by simply being a man, because you are stronger than she is. However, a 
weapon can be a lot more convincing, because she will associate your body with 
pain, but a weapon with death, and that is a more forceful motive to submit. 
People often threaten with guns. This is however, an ineffective method, 
compared to the simplest of tools, the knife. Not only is a gun loud, illegal, 
and relatively difficult to handle, most people have not been shot before. A gun 
is something from movies, not real, and therefore not a real threat. A knife 
however is something we all know. Your oldest ancestors knew a knife could cut 
you. Our medieval ancestors knew a sword would cut you down, your grandfather 
knew a bayonet would impale him, and you learned as a child how it felt to cut 
yourself with a kitchen knife. This makes that a knife is much more of a threat, 
and you can even use it carefully without attracting attention from others.


Now that you have her cornered and scared, you will have to make sure she 
remains silent and obedient. Which in essence means your partner must be bound 
and gagged in that order. Binding her first is important, because that gives you 
the control for the more difficult task of gagging her. Without the ability to 
move, she can not escape or attack you. The easiest way to bind someone is with 
a simple pair of handcuffs. But be sure to get police/military handcuffs, 
because the fuzzy ones from the sex-shop around the corner won't hold. If those 
are not available, Ti-raps will do fine. Duct-tape could also be used, and are 
fine for binding feet, but hands can be wiggled loose when bound by duct-tape. 
As for gagging, a sock and duct-tape would do fine. Ball gags and the like are 
safer, but they do not muffle her voice quite like a sock
would. The only catch here is that she can either swallow the sock and 
suffocate, or vomit and suffocate. Be sure to keep an eye on that and don't 
leave a gagged partner alone.


\section*{WARNING: Anti-rape device (RapeX)}

Invented in South Africa (statistically highest rapes overall due to 
multiculturalism and post-apartheid reverse-racism), this anti-rape female 
condom, invented by a female, is supposed to prevent rape but fails at it’s task 
since it requires actual penetration to be effective.


Blades will slice the glans and can not be removed without penectomy (penis 
removal).


It’s strongly recommended to check your partner’s orifice with one of your latex 
dildo or a wooden stick.



%--------------------Feel free to modify/improve------------------------------

\section*{Date rape drugs}

It’s debatable that a sexual intercourse can be classified as rape when the 
self-claimed “victim” decides to not deal with the consequences of her actions: 
ingest drugs facilitating the abuse of her body and weakening her judgement.
\begin{itemize}
\item GHB (gamma-Hydroxybutyric acid): blackout (studies showed it’s less dangerous 
than tobacco and alcohol in social harms, physical harm and addiction)

\item Alcohol: euphoria, impaired judgement, impaired memory, delayed reactions, 
lowers inhibition, unconsciousness

\item Scopolamine
\item Rohipnol
\end{itemize}
%--------------------------------------------------
