 
Knowing your terrain is everything for a successful coitus. Reading up on city 
maps and having a look on various closing times are crucial to a good escape 
plan, running from those who wish death upon our civilization. Have at least two 
escape routes or more when you and your partner is done with the coitus. Be sure 
your partner is in a safe location where he/she can be found, but isn't 
reachable for random people passing by; let them be at least a five minute walk 
from any major trail. Never engage in coitus, with anyone, within a close 
vicinity of your living ground, you might be recognized if you are to meet in a 
local store and after she were to go missing. Another option is having a 
temporary shelter for the night in case a search party is organized and set in 
motion, at that time moving on the streets by foot or car is not the best idea. 
Be mindful if the neighborhood is socially close and work together, or in the 
big city where people live more anonymously. You must also have a hiding place, 
a safe location for from any type of human interaction, underground or high up, 
where you can store various memorabilia, you may keep something that will erode 
with time never keep teeth or pictures, and a dumping place where you can burn 
up and erase the coitus suit and other coitus gear.


\section*{Disposing of Bodies}


From time to time you will find people who will figure out who you are and who 
you are unable to break mentally. If you happen to be in a situation where you 
need to kill your partner, here is a quick guide on how to dispose of the body.


\section*{The Dexter Method}

Put the dead body in a bathtub or shower and drain all the blood by slitting the 
thighs and neck. Blood is very thick and might clog your pipes. When the meat is 
dry, chop up the body into relatively small pieces and find a safe place to dump 
them. Ideally the ocean, or a forest. If you throw them out in the ocean the 
tides might wash them ashore. It is ideal to do some research of ocean streams 
and tides in your area and find one that goes outwards in the ocean. If you 
decide to bury it in the forest, it is very important to assure that the body 
decomposes as quickly as possible. Bring some coke, some yoghurt and a hammer. 
Knock out all the teeth, crush the fingertips and mix it all with coke or an 
acidic liquid. Throw yoghurt around the body to ensure accelerated decomposure. 
The bacteria in the yoghurt will eat away at the body and the acid in the liquid 
you chose will erode away the teeth and fingertips.


\section*{The Doggy Bag}

This is similar to the previous method, only without the drainage or the 
chopping. You will need a tool to remove teeth and fingernails, loads of yoghurt 
(If you buy too much of it, you will raise suspicion. Try buying some in 
separate places), a bottle of acidic liquid, a sleeping bag, a burial cross and 
a dog collar.

You start by digging a hole with a slope and place the body head first into the 
sleeping bag. Then you place the sleeping bag into the hole with the head 
downwards. Beforehand obviously remove teeth and fingertips. Place the teeth in 
the coke bottle while you are burying the body. Pour the yoghurt into the bag 
along with the coke and place the cross with the dog collar on top of of the 
bag. The dogs will not be fooled by this but, dogs are eventually going to try 
and dig up the body.  The owner is most likely to hold back the dog from digging 
when he sees the burial cross and the collar.