It must be stated that this is not a chapter that should be overlooked. 
Depending on whether you’re looking for a permanent coitus partner or a 
temporary one, whether you wish word to get out or to keep the encounter hush, 
there are many variables ranging from age, skin colour, temperament, religion 
and even bmi (body mass index). Children are popular as well and it should be 
noted that they are the most malleable of partners, second only to the mentally 
handicapped (should the deviant venture). As well, “Permanent” and “Natural” 
are two separate things in this particular passage, natural being fleeting and 
permanent being not.

On the subject of permanent coitus partners, either youth or old age are 
demanded. The elderly can easily be locked away while the young, with proper 
love and attention can be made to adore their master all the more. Particularly 
with the young, one should keep education to a minimum, lest they get ideas of 
the unnatural ways “normal” people get about. It should be considered a full 
time job to keep unwanted books and the like out of the hands of your fair 
lover. Chains and locks should not be needed after the first year; however, 
their mobility can be your enemy; so never allow knowledge of transportation 
and telecommunication to be passed to your partner. It has been suggested to 
make your own “Dungeon” before and having your own is not unheard of, or 
abnormal within the community.  Taking a permanent coitus partner has some 
risks involved but can be a highly rewarding experience as you watch them grow 
with you and love you unconditionally. Moving on, for natural coitus partners, 
one should begin with the humble bar. One night stands at bars, willing or 
“unwilling” will increase your libido and confidence committing this most 
natural act. The drunker your victim is, the easier they will be. One should be 
on the lookout for members of their entourage, as they can either add to the 
fun or cause trouble. The use of inhibiting drugs should never be used, there 
is nothing natural about killing your partner. At times, when you are ready, 
look for the member of the female herd called the “Designated Driver.” This one 
can be flirted with and brought outside. Without alcohol in her system she will 
prove a more interesting endeavor and given her designation as the most 
“responsible” she will be the least likely to share your stories of your love.

It is very important to choose a victim without many social contacts, or choose 
someone who works far away from home. For example, a woman that just comes at 
home for weekend because she works too far away. It is important to know as 
much about her as possible, but without being too obvious and without talking 
with her or people she know well. You can try to get information with common 
search methods on the internet, for example, if you get her email you can look 
if she is at Facebook or Reddit and look at her posts and comments to get some 
information about her. Also, study her everyday life: when does she leave home, 
and when does she come back? Where does she go to bed, and when she usually 
stands up? How often does she have contact with people at home, like friends 
and family? To get this information it is practical to break in her home and to 
place microphones and little cameras. Also load a keylogger, a screenlogger and 
a webcam logger on her computer, if she has one.

Although, you should aim to let your journey through the many joys of natural 
coitus be an enriching and diverse experience, at no point should you select an 
obese woman as a partner. Not because you may not be able to salute to the 
disgusting sloth, but more because the mass cannot be properly controlled 
during the encounter. And disturbingly, studies have shown that the mass can't 
even control itself: up to 45\% of obese women lose their bowels during their 
first natural coitus experience. Most scientists speculate that this strange 
effect may be caused by overwhelming fear conflicting with the overwhelming joy 
they have reported to feel over finally being selected for sexual attention. 
Others speculate that it is a finely tuned guidance system, evolved through the 
eons to show a male partner which roll he can open to proceed with the 
copulation.
%---------

\section*{The selection of outside prey and the necessary methods}


To engage in natural coitus is to bond. When a man forcibly enters a woman, 
they create an intimate spark between each other and one that is only removed 
with years of therapy and birth control. For most to-be “surprise lovers,” the 
biggest issue for them is that they have not yet found, “the one.” We as males 
have a primal desire for certain qualities in a woman. I could go on, crudely 
so, about the appropriate breast ratios and the evolutionary advantage to our 
cravings for wide, shapely hips and legs. However, it is better to be brief 
than babble. To put it simply, those who dismiss rapists as merely acting out 
of lust are very wrong. Power procreation is an act of much more than mere 
domination. It requires intricate preparation and love making skills along with 
a deep understanding of the desires of the female mind. One does not perform 
coitus out of desperation but, instead out of love. In our ever feminized and 
neutered society, women crave a man who is capable of taking what he wants.

It is therefore important to understand the meticulous selection patterns one 
must undergo in finding an appropriate partner. It might even be wise to sample 
multiple potential lovers in order to fully compare them with each other. The 
pattern of the screaming for instance, whether they begged to be killed or 
pubic hair length could all be significant factors in your choosing. I would 
not advise against taking age into consideration also. Has your future date hit 
puberty yet? Is she (or he) a member of a particular youth group? What is her 
sex life like? A good coitus experience requires a blend of different flavours 
and sources, and the key ingredients in your meal should be the character of 
your victim.

There are several interesting and unique methods in the surveillance of your 
partner to help better gauge your lover’s personality. I myself personally 
favor the Houdini approach and will solely cover this. However, there are far 
more are available on numerous websites. This tactic involves a much more 
direct involvement in the victim’s life, often coming to them directly posing 
in a variety of different roles. I remember for instance the time I disguised 
myself as a traveling door-to-door salesman! Poor Natalie was so shocked that 
she could barely stand up after the struggle-cuddle I gave her! However, a 
course of action such as this is best left to the more experienced lover, one 
who knows exactly how to manipulate a woman.

The basic principle of the Houdini technique is stealth through offense. By 
presenting yourself clearly to your victim, you are able to accurately study 
her life, social calendar and of course, personality. It is empirical however 
to choose wisely. It is very difficult to convince someone that the postman who 
just performed coitus on them is not just a close relative!  By selecting a 
position of power where you have daily access to them, you are putting yourself 
into a situation where you can effortlessly continue your examination. For 
example, popular choices include: teaching professions or internet 
personalities such as PewDiePie (A notorious enthusiast of the natural coitus 
and close friend of mine) or Tobuscus.

It is also vital to record your results on your present target. An easy table 
format is a great way to keep track of her qualities and best post-game plan to 
help keep her repressed and fearful. I’ve included a chart of mine below for 
reference.


\begin{longtable}{| p{0.3\textwidth} | p{0.3\textwidth} | p{0.3\textwidth} |}
\hline
\textbf{Date} & \textbf{Summary} & \textbf{Performance} \\
\hline
12/03/2010

Sandra

Power Flower Kindergarten
&
Sandra refused to cooperate in her Kindergarten game of finger painting and 
instead choose to play trains silently without her peers. This behaviour 
indicates a strong tendency to the anti-social.
&
8/10

A solitary woman is a proud woman. And it is the proud who make the best 
conquests. 
\\
\hline

13/04/2010

Sandra

Power Flower Kindergarten
 
&       

Sandra continues to display an extreme lack of hygiene. Today she vomited 
directly onto a supervisors lap and also was unable to go potty. A 
disappointing revelation.

&

4/10
A power lover must take pride in his achievements. A dirty catch is not one best 
boasted about.
\\
\hline

16/04/2010

Sandra
1539, Waltershire Avenue.
&        

After her first instance of guided intercourse Sandra continues to react badly. 
Frequent crying is unattractive and reveals a lack of decorum unbecoming for a 
five year old.
        
&

2/10

While a woman is the weaker sex some strength is still to be expected. Sarah 
did not meet these expectations.

\\
\hline

18/04/2010

Sandra

41 Bakers Street

&
  

Unable to give accurate updates as I am currently on on bad terms with the local 
police. Sandra has spoken to her parents and informed them of my surprise 
conquest.
        
&

1/10

No one likes a tattle tale.

\\
\hline

19/04/2010

Sandra
1539, Waltershire Avenue.
        
&

Police search has finally begun to die down. After a quick snoop of the house 
tonight, night it appears Sandra is playing with her dolls frequently again.
  
&
     

4/10

This is the fourth time this week she has played with those toys. I expect 
variety in my lovers.

\\
\hline

21/04/2010

Sandra

12 Battersea Ridge
       
 &

Review proves that Sandra is not an appropriate target to begin a coitus 
relationship with. Will update later with final meeting.
      
  &

n/a

\\
\hline

21/04/2010


Sandra
1539, Waltershire Avenue.
        
&

Sandra was unsurprisingly resistant at my attempts to coerce her. Regrettably, 
extreme force was necessary. Although her beauty is still intact, it is unlikely 
that Sandra will ever be able to ‘play dolls’ again without the aid of a pulley 
and lever system.
&    

2/10

Wheelchair bound is just another euphemism for too lazy to recover. I’m sure 
Sandra will walk this injury off.

\\
\hline
\end{longtable}

As you can see from the above chart, despite Sandra’s immense sexual potential, 
her weak personality let her down. By discovering this early, I was able to 
thankfully save myself the trouble of securing an appropriate chamber, 
‘restrictions’ and ball gag for her. This table should help highlight the 
importance of preparation and selection in the exciting and fast-paced world of 
natural coitus.