\section*{The look:}
The look plays a big role in the process of negotiation. You have to make sure that you're looking your partner in the eye, in order to make them feel comfortable and earn their trust. Try not to look angry or in a hurry, as this may be considered offensive in some cultures.
Your smile will also affect the emotional state of your partner, a warm smile with no teeth showing gives the best results, according to a German research team specializing on the effects of smiling at various species of animals.

\section*{The location :}
A friend of mine, Steve Robtorn, also a writer, once said: "Not every place is a good place." You have to choose wisely the place of your partner’s dream, and drag them into it. Use a blindfold on the way there to make it a cute surprise.

\section*{The time :}
Many men are too rushed, they try to end it as quickly as they can for fear of being noticed. This is wrong and insensitive! Your partner is enjoying it, no matter what they may be screaming to the contrary, and you need to make it last as long as you can. Try not to be selfish as this will ruin your partner’s enjoyment and that not what you want to do. Try moving your partner to multiple locations, using various methods of transportation (such as the trunk of a car). This will make it seem to last forever, and is key to achieving natural coitus.

\section*{The manner :}
We discussed above the time and we have to talk about the manner too. "Hard" is the word that should be floating in your heading in the time of the execution. A recent online poll from Jezebel.com showed that 97.8 percent of partners like it rough and hard, all the while denying this and yelling that they want out. The more you hear the word "stop", the more they want you to keep going. Who are you to leave their innermost desires unsatisfied?
