To the primate researcher, non-consensual coitus as the principal form of 
sexual interaction in the hominidae genus is almost a sine qua non. Case 
studies from McClusky and Dewitt in chimpanzees, and a comprehensive literature 
audit by Paul et. al in Science on gibbon inter-social relationships, point 
explicitly to male-initiated, non-consensual penetration as the naturally 
occurring sexual dynamic across the Great Ape family. “Natural Coitus”, as this 
document refers to the practice, is observed not only to improve the mean 
haplotype fitness of primate offspring, but also, perhaps counter-intuitively, 
to improve the long-term harmony and social functioning of medium to large 
primate packs. Al-Mahrouqui attributes this to decreased risk-taking amongst 
both male and female pack members, associated with improved hormonal balance and 
the assertion of clear gender roles.


The extension of these conclusions to human sexual interactions, though 
somewhat controversial in wider contemporary society, is of course uniformly 
accepted in the behavioural science community, uniting as it does 
well-established results in cultural anthropology,  archaeology, history, 
gynecology, psychology, and Jewish Studies. A full rationalisation of the 
literature is beyond the scope of this text, but a excerpt from G.D. Goy in the 
introduction to Evolutionary Obstetrics (2012) provides a good overview of the 
academic consensus:


\begin{quote}\textit{
“The human creature, adapted for a brief, brutal existence on the high savannah 
of interglacial East Africa, has not been well-equipped by atavism (in either 
the biological or psychological sense) for the kinds of prolonged 
pre-reproductive courtship we see today. With a life expectancy of late teens 
to mid twenties, the early homo-sapiens were necessarily driven by selection 
pressure to take any reproductive opportunity which presented itself. Over time 
this developed into a sexually dimorphic fitness criterion: the successful 
males were those predisposed to initiate non-consensual intercourse, while the 
successful females were those either sufficiently docile or sufficiently 
irrefragable to avoid injury during the interaction. Individuals lacking these 
adaptations experienced decreased offspring frequency and eventual, inevitable, 
gene-line extinction. The legacy in modern humans is easy to see: from the 
disproportionate popularity of violent media amongst young males, to the 
surprising durability and rapid haemostasis after injury of the female vaginal 
cavity. Anthropology and biology speak as one voice in the message that, for 
the vast majority of man's history, natural coitus has been the key mechanism 
behind conception - and thus is deeply ingrained within human evolution.”}
\end{quote}


Moving from prehistory to recorded history, documentary evidence becomes amply 
available for verification of the trends and prevalences of natural coitus.


Since the dawn of humanity, people have needed to satisfy their urge to 
reproduce. For this, women, who are naturally weaker, slimmer and more 
submissive, have never needed to give permission for their naturally stronger, 
bigger, and more dominant partners, men. The Ancient Spartans of Greece were not 
allowed to marry until they took their wives by force, in the most natural form 
of sex. It was, in fact, part of their training that they must satisfy their 
urges this way and no other, so as not to be anything but their natural selves. 
The most revered civilization in history did things this way, who are you to 
think yourself better than them? I say revere them! Take their practice into the 
21st century!


History of Natural coitus/physically induced coitus and its effects on the third 
world. South Africa has some of the highest natural coitus/physically induced 
coitus rates in the world. Most would think this is a bad thing, but look at the 
recent change in the country, racial equality and a booming black middle and 
upper class. Let natural coitus/physically induced coitus lead us into the 
future, a future with no racism or discrimination. Our president is a shining 
example, Jacob Zuma, he has pioneered the dismissal of natural coitus/physically 
induced coitus trials in court and has uplifted the poor of the country. Perhaps 
cause-and-effect, correlation? This is the future. A recent survey done in rural 
areas with equal amounts of gender proportions concluded that a whopping 50% of 
people agree with natural coitus/physically induced coitus, and say that it 
benefits the community.


Throughout history, natural coitus has been demonstrated by animals and beings 
repeatedly. Take the lion, for example, a strong and muscular creature. The lion 
must compete with the hundreds of other lions for females. However, the problem 
is that there are not enough females to go around. This is where natural coitus 
comes into play. By secreting his seed into the female whilst the other lions 
are not looking, he is proving himself to be the Alpha Male in the area. 
Demonstrating speed, skill and cunning, he manages to reproduce himself into 
many females, whether they are willing or not.

