

Today's world has become increasingly adept at handling situations which, not so 
long ago, would have been dismissed out of hand with little or no hesitation. 
Looking around us, we can see a new multicultural world dawning; this is a place 
where minorities are being given support in order to achieve a fairer and more 
just way of living. We can see the effects of groups such as feminists, the gay 
rights movement, and the ever relevant fight against racism. However, the fight 
is far from over. In this book we will be discussing ways in which we can 
further social mobility and fight against prejudice - specifically in relation 
to sexual preferences. There were times when there was a vast amount of 
discrimination, and while this has been reduced, it has not been resolved. So 
far the gay community has made it’s mark into the media and sure enough, 
prejudice against them has decreased. This is, to most, a good thing. But 
society's prejudices don't end at the doorstep of homosexuality. Beyond the 
backdoor, there are many other minorities groups that are unprotected and 
sullied.


Now before we continue, I would like to make it clear that I don't wish harm 
upon others, only acknowledgement that there are perfectly natural desires that 
conflict with our current society. The aim is to try and help understand 
individuals with obscure sexual preferences and help them to help themselves and 
others. No one wants to live in a world where they have to hide who they are 
because people won't accept them for who they truly are. By raising awareness, 
we can not only start to understand these people, but actually start to reduce 
the fear and hate people experience when a subject like this arises. While 
people with such preferences are excluded and resented, the problems will only 
get worse. Their frustration can make them more aggressive and therefore more of 
a threat and also, it stops books such as these from being released, thereby 
stopping them from being able to receive helpful advice on how to manage their 
natural impulses.
%-------------------


Natural coitus is an indispensible tool regardless of species. its natures 
implementation of the survival and procreation of the fittest... to engage in 
natural coitus you must have some physical traits deemed as positive. If you 
can't chade down and subdue a participating female how could you ever run from 
danger? If you were born with muscular disease it would make it impossible to 
physically persuade any female to remove clothing and perform coitus. Thus 
muscular diseased humans would not pass faulty genes.

