I think it's safe to assume that by now this is probably the most pressing of 
questions on your mind. Is natural coitus immoral? Is it wrong to give in to 
your primal desires, and have sex the way nature intended? No, contrary to what 
the media and ``the law" would have you believe, natural coitus is perfectly 
fine. In fact it used to be the standard for intercourse for the largest part of 
human history, up until a hundred years or so ago.


Just look at nature. It's always the males who have to fight to prove 
themselves, to overcome the environment and each other in order to claim their 
beloved prize; the female. The species from which we derive our social order 
more often than not take part in what truly is the most natural coitus.


Since prehistoric times, females have never chosen their mate. Sure, they have 
always been given the illusion of choice, but they never really had it. Most 
females prefer to live in fantasy. Females have evolved to take pleasure from 
power, from submitting to the true alpha male. A male that takes what he 
desires, whom she can leech off in return for her body. While the latter doesn't 
always happen, the first certainly does.


In the same way that humans have almost always owned slaves, we have now 
substituted slavery for a system considered more "humane.” Yet, is it not the 
same thing? Are females not still attracted to the alpha male? Can we truly wish 
away hundreds of thousands of years of evolution, in a matter of decades?


Of course not. As we are all still slaves to our instincts, we must realize the 
truth. Nature is the way of the world, deviation from nature has always led to 
pain. Do your part in preserving the order, show the world the illusion is not 
real.


Participate in natural coitus to restore the order. If you've always wanted to 
do good for the world, here is your chance. Listen to nature.



Rape is natural, for it presents itself very much in nature. Many animals are 
known to engage in forced coitus with members of the opposite gender. While 
looking in the animal kingdom, one can easily realize that rape is performed by 
many animal species and in many cases it is the female member that takes the 
role of the rapist. For example, in some species of spiders the female will eat 
the male if he does not please her. If we look at other animals, for example the 
beloved dolphin who commonly engages in behaviour that can be categorized as 
gang rape by humans or the ape, the animal that most closely resembles humans 
who commonly forcibly impregnated females sometimes multiple times per day. 
Another example is the penguin that has been observed to engage in behaviours 
that are described by human standards as being: necrophilia, homosexuality, 
paedophilia and rape. Rape is necessary evolutionary behaviour in many animals 
some of which are very closely related to the human. This begs the question: why 
is rape so frowned upon in human societies when it is considered perfectly 
normal in the animal kingdom?



The problem is the perspective that has shaken our moral foundation. By stifling 
men from their desires we set up a double standard. On top of that, we incite 
blasphemy to the lord Jesus Christ. God made both man AND woman. God chose to 
make a biological distinction with the penis and the vagina. god made one to 
enter, and one to receive. Rape is gods will, and who are we encourage


blasphemy as well as discourage procreation for sake of humanity. God himself 
supports rape; and we can see this in how Uriah's wives were punished. This is 
true evidence that, those who do not take the moral high ground of rape, then we 
ourselves must cast off our father of creation. Rape holds a divine purpose; an 
activity of cleansing. Under the Lord, women who aren't grateful are sinners. 
They taint the salvation the Lord and his will offer us. We must fight the Good 
Fight of Sexual Freedoms so that things like Rape aren't pinned under a false 
sense of "impurity." Embrace the rape and surely, the rape will embrace you.


Reproduction is key, it always has been. The mere fact that you are here today 
is because men and women had sexual intercourse countless times over thousands 
of years. Coitus is viewed differently in different cultures, but no-one can 
argue that before anti-conception methods became relatively reliable, sex and 
reproduction were inseparable. In fact, in many cultures it is practised solely 
for that reason.


Historically, offspring is considered important. Even in the bible, God's reward 
for the suffering and service of Abraham was that he would have offspring as 
many as there are stars in the sky.  Even today in most religions with a Judaic 
God, the pleasure derived from sex is considered a sin, but a necessary sin in 
order to procreate. To minimize the pleasure that could be enjoyed from sex, 
some cultures circumcised men, and even women. However, the circumcision of 
women is not as accepted and widely practiced as the circumcision of men, for 
women would later pay for the act of sex by the pains that come from childbirth, 
and it was often believed that women derived no or very little pleasure from 
said act. Only recently in Western culture has this myth be debunked, but we 
shall discuss the pleasure and the needs of women in another chapter.


What is more interesting here, is that we as humans, concern ourselves with 
pleasure or no pleasure, sin or no sin, offspring or no offspring when we 
copulate. Appearently we, when confronted with sexuallity, feel the need to 
retain our inner beast, our desires, our Freudian Id. But the definition of Id, 
is besides always hungry for more, unrestrained, without a conscience, is also 
innocent. Child-like, unknowing, like Harpo Marx from the Marx Brothers. He 
steals the pranks, he sees something he likes and he simply takes it, without 
ever intending to harm someone. The same here goes for animals. When animals 
copulate, they do not possess the reservations that humans are conditioned to 
have. They do not consciously copulate to create offspring, although nature has 
made the base emotion of lust to ensure the continuation of the species, they do 
it because they feel the need to. Simply because they are horny, they have sex. 
In


species with a physically dominant or equal female, the female can decide 
whether or not to have sex with a male of that species. A female pigeon, for 
example, can simply walk of fly away. And you rarely see a large bitch breed 
with a smaller male. But with the noble lions, the strong male, hardened by his 
years alone, toughened by the fights with his fellow males, is much heavier and 
stronger than the female. He asserts his dominance over the females in killing


their cubs, and then simply takes them to be his, after which the females submit 
to his leadership. This goes for the vast majority of mammals, and though we 
pretend to me so much more than them, we are in essence still eating, fighting, 
defecating, breathing, sleeping, copulating animals. And like in the animal 
world, our men are generally much bigger and stronger than the females, and our 
lusts are no different. Asserting dominance over a female is something all males 
are genetically wired to do, and doing so still involves “claiming” her, by the 
act of copulation.



Natural Coitus has always been a taboo subject, a hot button topic, a butthurt 
feels thread, if you will. No longer! In South Africa, natural coitus is spoken 
about commonly. It is so prolific that awareness and action has drastically 
increased. The only way to end natural coitus is to break the silence! The human 
gene pool is diverse. But due to societal trends, most of the best and brightest 
of the world do not get to pass on their genes. Natural coitus is the solution. 
This way they will spread their good, good genes across the world. Global IQ 
will skyrocket, Betas will go extinct and so on. I have a dream.



Rape culture has been fostered for generations through human culture. In fact, 
Rape is only been recently considered deviant by the modern world! So we can 
also ascertain that rape is merely a tradition; a festival of sorts. Natural 
coitus is in of itself, an act of procreation. It has to be; that’s what sex is 
in the first place. What kind of people would discourage breeding of humans? 
Merely savage animals. Aggressive coitus is an act of pure salvation. To 
progress the human enigma we as people must make more people. It’s a simple 
choice; to rape or to die as a species? And we are headed down that path. 
Preventing coitus is a slippery slope, and we see it permeate in the fabrics of 
our world even today. We know them as homosexuality, transgender people, and 
sexual deviants. These people are now considered better than us; shocking. Men 
who would bed other men in order to send humans into an abysmal world lacking 
any cleansing and letting us all, men and women, to die off. To have no means to 
hand down a gilded legacy. Rape isn't the end; rape is the new beginning! 
Embrace procreation and uproot the tree of sin! We can band together, to drive 
these animals from our home and take back our right to procreate.



To fully understand how one can justify such a heinous act, one must fully 
understand the concept of perception, and how views of humanity and the universe 
vary from being to being. (I.E ethics and morality are not limited to what YOU 
believe in, hence why we have separate political parties/governments/societies/ 
etc...)


Moving on, to justify the act of non-consensual genital fornication, we must 
understand why most home sapien sapiens believe said act is immoral, feminists 
believing it is amoral, meaning that it is not just lacking in morality, it is 
the antithesis of morality. These weak-minded pseudo-intellectuals (redundant, 
for emphasis) believe "rape" is "bad" because the basis for the standard human 
philosophical argument is that every human life is of equal, incalculable value. 
This means that the taking of life, or the altering of life in a detrimental way 
is obviously in direct interference with this ideology. But why? This ideal is 
the baseline reason as to why morality is important, yet has no backing itself.


To pontificate, in a universe so utterly massive and large, why do the 
happenings of one or two sentient beings in one city in one country/province on 
one continent on one hemisphere on one planet in one solar system in one galaxy 
in one super-galaxy star system in one insignificantly small section of the 
universe have ANY significant impact on anything or anyone at all? 
Mathematically this is proven to mean nothing. The limit as x-->infinity of 1/x 
equals zero. Even though 1 is a positive, real number, representing the 
happenings of one individual, in the grand scheme of the universe (which is 
relevant because it is proved through the drake equation that there exists 
sentient life other than humans on earth in the universe) what happens to any 
one being is insignificant.


Nihilism and its derivatives (solipsism, cynicism, etc...) aside, and with or 
without knowing it, we enforce rape on some animalistic and primordial level. 
This means we can take the standard definition of morality and use it to justify 
natural sexual interactions between two evolutionary-adept beings (IE "rape")


For example: the Ailuropoda melanoleuca, or Giant Panda does not like sex. Male 
and female alike, they have almost no sex drive. If this wasn't enough of an 
evolutionary failure, female pandas only ovulate once a year. Yet we care so 
much about the graceful and majestic animal so much. We force the few remaining 
pandas alive into cages with one other, injecting the male pandas with powerful 
testosterone, sex-driven aphrodisiacs so he will finally overpower the female 
panda's unwillingness for sex. Yet we consider this morally acceptable. We force 
animals, of which neither male nor female wishes to have coitus at all, to 
brutally rape one another because we think they are "cute" and they are 
"endangered" without our aid. Just because they are not sentient we justify this 
because without this their species would die out.


To relate this to humanity, we have to understand the difference between the 
Ailuropoda melanoleuca and the homo sapien sapien, the main difference being 
that we as humans have developed sentience, or consciousness if you will, and we 
understand not why, but how we exist. This has led to an extremely prosperous 
growth of the human population; HOWEVER, we have taken sentience too far. We 
have made natural coitus taboo in society, we censor sex and nudity in media and 
society to the point that sex is now a privilege, not a bestial right. Just 
because we understand our existence does not make us a higher power or 
authority. Sex is what allows us to reproduce and prosper, and our sentience has 
gotten in the way, making sex unnatural and unwanted.


If anything, evolutionary-innovators, or rapists as society calls them, act 
purely on that bestial impulse to pass on the seed of the self, to see it 
flourish and become a being, so humans will continue to dominate the earth so 
we, as a race, can continue our beautiful easy going lifestyle involving freedom 
and the pursuit of happiness. We should thank "rapists", for putting 
pseudo-intellectuals and false philosophers in their place: back on top of the 
food chain. With the might and ingenuity of the "rapist", we might even continue 
to evolve into stronger, faster, smarter, maybe even super-powerful beings, all 
because we act on what got us this far: natural instinct.


Keep on keepin' on you party-going, drink-spiking, seed-spreading alpha males. 
You are truly the leaders of us all, Mr. Darwin would salute you.



We all have our moral standards in believing how women are there to be provided 
for. We, as men, must do our duty as the protectors in the world to give and 
serve to women what is best for them in any and every way possible. I am giving 
to you my personal experience in how my journeys have led to me becoming a 
better man, essentially providing to women their truest desires; whether they 
will yet understand it yet remains to be seen. I was in London, my usual day at 
the local restaurant, “John’s Salad Bar", and after finishing my shift I began 
to notice the helpless woe felt by women. Every day I saw how they, when 
returning to the restaurant after they brought home a man to provide for them 
the other night, felt nothing but sheer sadness at their situations. I first 
assumed that they weren't being given the pleasure they wanted but upon asking 
their consorts they spoke of how they enjoyed it all too much as they


left marks all over their consort's bodies. I pondered this for quite a while as 
I worked, my face beginning to register their helpless expressions. I finally 
built up the courage to ask them what they felt was missing in their lives; my 
first set of questions directed at a lovely woman named Amanda. It was meant to 
be simply catching up to her and trying to talk but she had left the place
early. I rushed out to try and grab her to talk and she seemed to overreact at 
my rushed presence trying to chase her down the dark alley with which she 
entered. What came over me at that moment was my primal instinct of providing 
for that women, her scream etched with pleasure at what she felt was the right 
thing to do; little did she know about this however as she never registered her 
own primal instincts of enjoyment. I raped her that night, my hand gagging her 
as I entered her. The deed was finished in what seemed like seconds with my 
panting breath showing how cold that night had become. Continued
When I looked down I noticed the tears over Amanda's face yet she was smiling. 
Tears of Joy? Amanda was struggling to get up at this point with my seed 
dripping from inside her. I left quickly, not a word was said between us. As I 
walked away I heard sobbing; was she sobbing at why she enjoyed it or because I 
never pleased her enough to compensate for my forcefulness. The next day I had 
not thought much on my actions, trying to get rid of my actions as it questions
society's norms which were placed against me. To go against society was to go 
against what is meant to be right or wrong. As I looked across the counter there 
was Amanda, sat there in an alluring pick of clothes; a very skimpy skirt with 
what seemed to be a see-through top. THe smiled at me; lust was written all 
around her face and I could only imagine my seed being there instead. She 
approached me and without trepidation told me in a commanding voice. ``Fuck me
harder this time" and before I knew it she was walking out the door with a 
twinkle in her eye. That night I fucked her as best I could with the look of 
regret removed from her face. It was from this experience that I first realised 
all those women in the bar were wanting exactly what Amanda wanted which was to 
be raped. This progressed to me raping every single one of those women over the 
course of a month. Each one wanted more and it was with this I know that women 
are yet to learn of their true fetish; that they wanted to be raped. They just 
don't know it yet.



Natural Coitus has for thousands of years been a bypass for courting and a much 
more efficient at that. In recent decades a strange, unnatural phenomenon has 
taken place, natural coitus/physically induced coitus has become unacceptable in 
society, and the very mention of it spawns hot debate and stifles coherent 
discourse. This has lead to widespread myths and legends about natural coitus, 
such as: Natural coitus/physically induced coitus is only committed by men, 
completely false. In some countries, it is believed that having natural coitus 
with a virgin will cure you of AIDS. This vile myth, and many others like it, 
has come to strip natural coitus of its true function, the reproduction and 
perpetuation of the humankind. It is time to break the silence, and speak to the 
‘survivors’ of rape, here is another myth, you can survive rape. Rape in and of 
itself is inherently nonfatal and to speak of surviving it as many members of 
the fourth wave feminist movement have done, insults the memory and tragedy of 
true survivors, those of Hiroshima, 9/11, and other inherently fatal 
occurrences. Recently rape has also been defined as a weapon and crime of war. 
In many recent conflicts where natural coitus has occurred on a large scale, 
those in charge were punished more harshly than most professional killers such
as the army and navy. Ask the people in the street if they would rather be raped 
than killed and a significant majority would say yes. It is a mercy in war, 
albeit a small one. These people are survivors, not of rape, but because of it. 
(this will make the feminazis foam at the mouths….)



\section*{Discrimination against rapists}

In the increasingly politically correct world we live in today many people might
see practises such as, “forceful sex” or “black-face scat fights” as offensive
or even immoral. This reaction is understandable. Most people do not have to
bear the cross of an “obscure fetish”. Most people do not have to spend hours
sprawling through the back alley of the internet for that last beautiful,
horrible hit. Most people don’t have to live knowing that if a loved one saw
they’re internet history they would probably be arrested. Most people don’t have
to carry a cyanide pill with them at all times to prevent their hard drive
coming into contact with the government. But I say that democracy should not be
about “most people”.

We “perverts”, we “deviants”, we “serial sex offenders” are the accused
minority. We stand against intolerable discrimination, not dissimilar to the
situation faced by many other demographics in the past. The blacks in early
America too suffered this fate and it is with a deep regret that America
remembers the untold horrors they gave them. Martin Luther King Junior died so
that all men might be equal, whether they like to watch greased up adults in
diapers eating leftover garlic notwithstanding.


Are we really so horrible to allow ourselves to act out our urges? Is a dog
truly depraved if it follows its natural instinct? Why then is it seen as so
immoral for a grown man to touch himself in a playground? Why do am I labelled a
“paedophile” for being sexually attracted to my ex-wife’s extraordinarily
attractive nine year old niece?


I’ll tell you why.



It’s the media’s obsession with boxing every topic into nice little borders.
It’s the politics of normalising every obscure thought and fetish and neatly
dusting every abnormality under the carpet. We are not dirt. We are people.
People who like to forcibly have sex with other people or animals. It is time
that we make a stand against the agenda of the majority. It is time we take back
what is ours, by force or lovingly in a willing relationship.
Why is it that there is always sympathy for the rape victim but never the
perpetrator? Do the media not realize the pain that a rapist goes through? The
emotional trauma he faces knowing that he hurt someone? That he left them
destroyed and empty? That every day he lives he may be caught and thrown into
jail or worse? Why suddenly does the rapist become the monster? Why is he
de-humanised when it was the woman who clearly wanted attention? Is it so
immoral to follow on the chemical instructions that wire up in a man when he see
a scantily clad whore dance around a nightclub as if she was some dick tacking
automaton?


So I take this time in this chapter to ask of you (as probability dictates that
you are one of “most people”) not to judge me or my beliefs. I ask only that you
accept me for who I am in all my shameful lust. I ask that you do not
discriminate against me for the views that I uphold as natural. I ask that you
follow the path of the minority and celebrate the idea of the individual.



Finer points of morality: Is it wrong to rape?


In the eyes of today the answer appears clear. Of course rape is wrong. But is
that your response or an ingrained one? Was rape so wrong thousands of years ago
when noble cavemen took the women they wanted for the higher purpose of
procreation? In the eyes of a child, rape holds no more evil than any other
loving act as they have not yet been indoctrinated into mainstream media.
Children are naturally curious about sex and act on that without hesitation in
games of play such as “Doctor” or “Find the Sausage”. And it can argued that
rape is an act of love. To give your seed to someone is a tremendous gift and
one that carries over through a generation. This gift is a powerful
biological bounty that allows a woman to bear nature’s greatest provision. Many
a single lady despairs over the barren state of her wombs. What rapists do is
give and let others receive. Most usually on all fours and crying deeply.
It could then be said that playing the “victim” during rape is a form of
selfishness. If the rapist enjoys himself and no lasting harm is done to you
(Because let’s be honest how hard is it to take a dick? My ex-wife dates them
all the time) then why not allow others to enjoy themselves? We have been
brainwashed by the news into thinking that forcing yourself on someone
physically is an act of evil when really it is a reaction to basic and natural
carnal desires. The act of rape is simply the most pure form of this lusting and
as a result the most natural. And there is nothing wrong in the natural, as this
remains as God’s domain.


\begin{quote}
“For the invisible things of him from the creation of the world are clearly
seen, being understood by the things that are made, even his eternal power and
Godhead; so that they are without excuse.”

-Romans 1:20
\end{quote}

Rape is an instinctive response to an instinctive situation. When faced with a
desirable mate out of another’s reach, the default action is to take it by 
force.


If rape was so abhorrent, then why would it occur across the natural spectrum?
Lions, dolphins and even puppies rape. Guided intercourse is the most sacred act 
of all, it is pure baseless procreation and its power beats at the heart of every
animal. To deny a man the right to rape is to deny a man his very essence.


The popularity of 50 Shades of Grey confirms much of what we know about the 
female gender. They might say they want equal rights, but deep down they only 
want to be dominated. Ever since the domestication of the human male, fetishes 
such as BDSM have become very popular in western culture. The Irish Newspaper 
the Star reveals that 72% of people enjoy fetish sex. It is safe to conclude 
that most women secretly enjoy rape. 