During my travels, I have come across many different people and, more 
importantly, types of people. Everyone has a preset of opinions { such is human 
nature } and there are always those who militantly oppose the decisions and 
lifestyles of others, even when said individuals in no way impact their own 
lives or sovereignty. Such narrow-minded people simply cannot be reasoned with. 
The most efficient course of action is to simply ignore them, as this causes the 
least amount of hardship to both them and yourself.


We as humans must make allowances for the less capable, we are told - a policy 
drummed into us from a young age. The idea that your own opinion is 'correct' is 
often referred to as delusion, and this what I will refer to it as throughout 
this chapter.


Now, most human beings assume that their view of the world is the correct one. 
This is an arrogant assumption to make as there is no 'right' or 'wrong', merely 
one's own way. False morality is often used as a hammer to beat down those who 
do not conform. Those of us wishing to upset the status quo must resign 
themselves to bear the brunt of the ossified legal system, and the wrath of the 
majority if we are caught furthering mankind in this way. As far as opinions go, 
all are subjective. To bog oneself down in endless moral dilemmas is to 
purposefully ignore the joys of living free and claiming for yourself what 
nature has rightfully bestowed upon you. Human interactions are often 
characterized by dominance, and natural hierarchies are just that; natural. This 
is true for both the micro and macro-level strata of human civilization.


Delusion comes in many forms, however the most dangerous one is aggression. An 
emotion widely used by feminists to fuel their many smear campaigns, it is the 
driving force of all delusion within the feminist regimes. They feed on it like 
maggots on rotting flesh, and it empowers them in their crusades against the 
stronger, more noble sex. It is important I stress the link between delusion and 
feminists, as that is at the very core their zealous religion.


A topic raised time and again by feminists everywhere is Natural Coitus, however 
they are usually portraying a skewed, exaggerated, or a downright untruthful 
version of it, claiming the Natural Coitus is actually harmful to females and 
the female 'race' of 'womyn' as a whole. Nothing could be further from the 
truth.


When tackling with these feminists it is extremely important to treat them with 
a degree of sympathy, as feminism itself is a well-known mental disorder. Those 
poor souls, in their never-ending and joyless quest to usurp from man his 
rightful place, know not the ecstatic bliss they so foolishly disregard in order 
to chase after unattainable goals and insatiable appetites of the most material 
sort.


A woman's whole existence revolves around subjugation. She is a vessel of the 
man's seed, and it is her divine duty to submit to a strong man. Her place is at 
his feet, chained to his fate by his own iron will, and ready to service him in 
any and all ways he wishes. Modern feminism long ago abandoned these sacred 
tenets of the age-old covenant. As a result, their foolishness has wreaked havoc 
on the whole of society.


Women, being the limited creatures that they are, cannot accept that Natural 
Coitus is, and always has been, a process of demonstrating the natural hierarchy 
within a society. This simple fact is demonstrated time and again by animals in 
the wild. One example would be bears, who perform Natural Coitus quite often, 
and to such an extent that it is seen as completely acceptable so long as the 
Male bear has already asserted its dominance.


If approached by a feminist, it is often regarded a necessity that you 
immediately proclaim the following words, 'Natural Coitus is the way of the 
world'. This demonstrates you are enlightened to a higher level of 
understanding, and as a result you are actually of a higher social status and 
are fundamentally a better person than they are. Usually this unsettles even the 
most hardened of feminists.


If this approach doesn't work it is best to retreat to a pre-arranged tactical 
location and avoid contact, as feminists, once pushed, can rarely be reasoned 
with. Then again, they make prime coitus candidates, as their very nature belies 
weak women who yearn for a strong male figure to come into their lives and 
literally sex them into submission. Explaining this to them is almost 
impossible, which is why, in the case at least, words should give way to deeds.