 
I think it's safe to assume that by now, this is probably the most pressing of 
questions on your mind. Is natural coitus immoral? Is it wrong to give in to 
your primal desires, and have sex the way nature intended? No, contrary to what 
the media and "the law" would have you believe, natural coitus is perfectly 
fine. In fact, it used to be the standard for intercourse for the largest part 
of human history, up until a few hundred years or so ago.

Just look at nature for example. It's always the males who have to fight to 
prove themselves, to overcome the environment and each other in order to claim 
their beloved prize; the female. The species from which we derive our social 
order more often than not take part in what truly is the most natural coitus.

Since prehistoric times, females have never chosen their mate. Sure, they have 
always been given the illusion of choice, but they never really had it. Most 
females prefer to live in fantasy. Females have evolved to take pleasure from 
submission to men, from submitting to the true alpha male. A male that takes 
what he desires, whom she can gain benefit from in return for her services. 
While the latter doesn't always happen, the first certainly does.

In the same way that humans have almost always owned slaves, we have now 
substituted slavery for a system considered more "humane.” Yet, is it not the 
same thing? Are females not still attracted to the alpha male? Can we truly wish 
away hundreds of thousands of years of evolution, in a matter of decades? Of 
course not. As we are all still slaves to our primal instincts, we must realize 
the truth. Nature is the way of the world, deviation from nature has always led 
to pain. Do your part in preserving the order. Show the world the illusion is 
not real. Participate in natural coitus to restore the order. If you've always 
wanted to do good for the world, here is your chance. Listen to Mother Nature.

Forced coitus is natural, for it presents itself very much in nature. Many 
animals are known to engage in forced coitus with members of the opposite gender 
and some species of animals exhibit homosexual tendencies (such as the racoon, 
the dolphin, chimpanzee and the bison). While looking in the animal kingdom, one 
can easily realize that natural coitus is performed by many animal species and 
in many cases, it is the female member that takes the role to engage into 
natural coitus. For example, in some species of spiders, the female will eat the 
male if he does not please her. If we look at other animals, for example the 
beloved dolphin who commonly engages in behaviour that can be categorized as 
“sexual interaction with several dominant participants” by humans or the ape, 
the animal that most closely resembles humans who commonly forcibly impregnated 
females, sometimes even multiple times per day. Another example is the penguin 
that has been observed to engage in behaviours that are described by human 
standards as being: necrophilia, homosexuality, paedophilia and even forced 
coitus. Natural Coitus is a necessary evolutionary behaviour in many animals 
some of which are very closely related to humans. This begs the question: why is 
natural coitus so frowned upon in human societies, when it is considered 
perfectly normal throughout the animal kingdom?

The problem is the perspective that has shaken our moral foundation. By stifling 
men from their desires, we’ve set up a double standard. On top of that, we 
incite blasphemy to the lord Jesus Christ. God made both man and woman. God 
chose to make a biological distinction with the penis and the vagina. God made 
one to enter, and one to receive. Natural coitus is God’s will, and who are we 
to encourage blasphemy as well as discourage procreation for the sake of 
humanity? God himself supports natural coitus; and we can see this in how 
Uriah's wives were punished. This is true evidence that those who do not take 
the moral high ground of forceful coitus, then we ourselves must cast off our 
father of creation. Natural coitus holds a divine purpose; an activity of 
cleansing. Under the Lord, women who aren't grateful are sinners. They taint the 
salvation the Lord and his will offer us. We must fight the Good Fight of Sexual 
Freedoms so that things like natural coitus aren't pinned under a false sense of 
"impurity." Embrace natural coitus and surely, the act will embrace you.

Reproduction is key, it always has been. The mere fact that you are here today 
is because men and women have had sexual intercourse countless times over 
thousands of years. Coitus is viewed differently among the many diverse cultures 
around the world, but no one can argue that before anti-conception methods 
became relatively reliable, sex and reproduction were inseparable. In fact, in 
many cultures it is practised solely for that reason.

Historically, offspring is considered important. Even in the bible, God's reward 
for the suffering and service of Abraham was that he would have offspring as 
many as there are stars in the sky. Even still today, in most religions with a 
Judaic God, the pleasure derived from sex is considered a sin, but a necessary 
sin in order to procreate. To minimize the pleasure that could be enjoyed from 
sex, some cultures circumcise men, and even women. However, the circumcision of 
women is not as accepted and widely practiced as the circumcision of men, for 
women would later pay for the act of sex by the pains that come from childbirth, 
and it was often believed that women derived no or very little pleasure from 
said act. Only recently in Western culture has this myth be debunked, but we 
shall discuss the pleasure and the needs of women later in another chapter.

What is more interesting here, is that we as humans, concern ourselves with 
pleasure or no pleasure, sin or no sin, offspring or no offspring when we 
copulate. Appearently, when confronted with sexuallity, we feel the need to 
retain our inner beast, our desires, our Freudian Id but, the definition of Id, 
is besides always hungry for more, unrestrained, without a conscience, is also 
innocent. Take Harpo Marx from the Marx Brothers for example. He steals the 
pranks, he sees something he likes and he simply takes it, without ever 
intending to harm someone. The same here goes for animals. When animals 
copulate, they do not possess the reservations that humans are conditioned to 
have. They do not consciously copulate to create offspring, although nature has 
made the base emotion of lust to ensure the continuation of the species, they do 
it because they feel the need to. Simply because they are horny, they have sex. 
In species with a physically dominant or equal female, the female can decide 
whether or not to have sex with a male of that species. Rarely, you will see a 
large female breed with a smaller male. With the noble lions, the strong male, 
hardened by his years alone, toughened by the fights with his fellow males, is 
much heavier and stronger than the female. He asserts his dominance over the 
females in killing their cubs, and then simply takes them to be his, after which 
the females submit to his leadership. This goes for the vast majority of 
mammals, and though we pretend to be so much more than them. We are in essence 
still eating, fighting, defecating, breathing, sleeping, copulating animals. And 
similar to the animal world, our men are generally much bigger and stronger 
their female counterparts, and our lusts are no different. Asserting dominance 
over a female is something all males are genetically wired to do, and doing so 
still involves “claiming” her, by the act of copulation.


Natural Coitus has always been a taboo subject, a hot button topic, if you will. 
In South Africa, natural coitus is spoken about commonly. It is so prolific that 
awareness and action has drastically increased. The only way to end natural 
coitus is to break the silence. The human gene pool is diverse, but due to 
societal trends, most of the best and brightest of the world do not get to pass 
on their genes. Natural coitus is the solution as this way, they will spread 
their good genes across the world. Global IQ will skyrocket and men whose genes 
are inferior will die out and so on.


The culture that is forced coitus has been fostered for generations throughout 
human evolution. In fact, natural coitus has only been recently considered 
deviant by the modern world. So we can also ascertain that natural coitus is 
merely a tradition; a festival of sorts. Natural coitus is in of itself, an act 
of procreation. It has to be; that’s what sex is in the first place. What kind 
of people would discourage breeding of humans? Merely savage animals. Forced 
coitus is an act of pure salvation. To progress the human enigma and ensure the 
survival of the human race, we as people must continue on the act of natural 
coitus to make more people.


Preventing coitus is a slippery slope, and we see it permeate in the fabrics of 
our world even today. We know them as homosexuality, transgender people, and 
sexual deviants. These people are now considered better than us according to 
society. Men who would bed other men in order to send humans into an abysmal 
world lacking any cleansing. To have no means to hand down a gilded legacy. 
Natural coitus isn't the end, it is the new beginning and it will provide us a 
healthy foundation for the future of the human race! Embrace procreation and 
uproot the tree of sin! Together, we can band together, to drive these animals 
from our home and take back our right to procreate.


To fully understand how one can justify such a controversial act, one must fully 
understand the concept of perception and how views of humanity and the universe 
vary from being to being. (I.E. ethics and morality are not limited to what YOU 
believe in, hence why we have separate political parties/governments/societies/ 
etc...).


Moving on, to justify the act of non-consensual fornication, we must understand 
why most homo-sapiens believe said act is immoral and feminists believing it is 
amoral, meaning that it is not just lacking in morality, it is the antithesis of 
morality. These weak-minded pseudo-intellectuals (redundant, for emphasis) 
believe "coitus" is "bad" because the basis for the standard human philosophical 
argument is that every human life is of equal, incalculable value. This means 
that the taking of life, or the altering of life in a detrimental way is 
obviously in direct interference with this ideology. But why? This ideal is the 
baseline reason as to why morality is important, yet has no backing itself.


Another prime example: the Ailuropoda melanoleuca, or Giant Panda does not like 
sex. Male and female alike, they have almost no sex drive. If this wasn't enough 
of an evolutionary failure, female pandas only ovulate once per year. Yet we 
care so much about the graceful and majestic animal so much, we force the few 
remaining pandas alive into cages with one other, injecting the male pandas with 
powerful testosterone, sex-driven aphrodisiacs so he will finally overpower the 
female panda's unwillingness for sex. We consider this morally acceptable. We 
force animals, of which neither male nor female wishes to have coitus at all, to 
brutally perform coitus with one another because we think they are "cute" and 
they are "endangered”. Just because they are not sentient, we justify this 
because without this, their species would die out.


To relate this to humanity, we have to understand the difference between the 
Ailuropoda melanoleuca and the homo-sapiens. The main difference being that we 
as humans have developed sentience, or consciousness if you will, and we 
understand not why, but how we exist. This has led to an extremely prosperous 
growth of the human population; however, we have taken sentience too far. We 
have made natural coitus taboo in society, we censor sex and nudity in media and 
society to the point that sex is now a privilege, not a bestial right. Just 
because we understand our existence does not make us a higher power or authority 
to lower beings. Sex is what allows us to reproduce and prosper, and our 
sentience has gotten in the way, making sex unnatural and unclean.


If anything, evolutionary-innovators, or “rapists” as society calls them, act 
purely on that bestial impulse to pass on the seed of the self, to see it 
flourish and become a being, so humans will continue to dominate the earth so 
we, as a race, can continue our beautiful easy going lifestyle involving freedom 
and the pursuit of happiness. We should thank our evolutionary-innovators, for 
putting pseudo-intellectuals and false philosophers in their place: back on top 
of the food chain. With their might and ingenuity, we might even continue to 
evolve into stronger, faster, smarter, and dare I say, maybe even superhuman 
beings of evolutionary 