
    One trend I have noticed recently while collecting information for this book, is the suprising number of women
who have decided to develop relationships with their rapists. Women in the modern era want a ``real man", you will often
hear this said and linked over social networking sites. A real man rapes, and women deep down know this. Any time you
hear a woman saying that she wishes she had a ``real" man , or that all of the ``real" men are gone, this is woman speak
for ``sheesh won't someone rape me already?".


        It may sound funny, but data points to this being one of the easiest pieces of information to derive from our studies.
Case in point, Donna Summers. Mrs. Summers was walking home from her local bar on the night of April 17 2010, when suddenly
while traveling down a dark alley way, she was approached by a man from the bar she had seen earlier that night. The man, Allen
Roostle, had over heard Donna complaining to her friends that there were no 'real' men in this bar, and that she was going
to head home early for the night. Needless to say, Allen raped Donna that night, repeatedly, leaving her beaten and bleeding
in the alley, and unknown to her at the time pregnant with Allens child.


        ``Many women would of called the police or a support line" Donna told us, ``but not me.. there was something about
what happened that made me realize what I had been looking for all along, a man who was not affraid to take what he wanted,
when he wanted.. how he wanted it." This lead Donna on a rare hunt, she needed to find her rapist to continue their relationship
but could not involve the police. She went online and was suprised to learn that there were indeed various internet forums
for just this reason, women who were raped and now wanted to continue contact with their rapists. She would of been more suprised
if not for her own feelings of attachment.


        Through the website Donna was able to make contact with Allen ( it turned out Allen was a long time member of the site
and had raped a large precentage of it's female membership) and after arranging some more ``dates" together, Donna persuaded Allen
into a long term Rapelationship. A rapelationship is a term I have created to define the modern occurence of women realizing
that while our society and minds have evolved rapidly, sexually women still yearn for rape and studies show it is the
best foundtation to begin a relationship wth. Donna and Allen are still together, and he has been monogamously raping her
since they had their first romantic encounter in that dark alley.


        The key to happiness is to find your own rapelationship, and give it the time and care that you would to any other facet
of your life. Often, then woman who is on the receiving end of your rapelationship will come to appreciate what you provide: giving
her that feeling of what it feels like to be a good woman, submissive and eger to please her male counterpart. Any time
the woman decicded she is going to make a decision that does not comply with your commands, simply look directly into her
eyes like the first time you raped her, and she will be puddy in your hands.


        Edgar Brussels, a rapelationship counselor for the past twenty four years residing in Toronto, had this to say on the subject.
``While at first many couples come to me with the woman having a scared and defiant look in her eyes, over time after the female
end of the rapelationship has learned not to anger her master, and has learned to cook his favorite foods and keep the living
area to the mutually agreeded upon level of cleanliness, after all this has been done-- the fear and independence in the females eyes
melt into a complacency that is a marvel to witness." Edgar goes onto say ``the core of every rapelationship is the realization
that the female must submit to her rapists evey whim, and that the male must rape the female every chance he gets, for the more she
is raped the more she will come to love her rapist, and thus her rapelationship."


        Modern day women have forgotten the bliss that rape can bring to a rapelationship. Organizations around the country
teach women that rape is wrong, and the men who commit rape are criminals, often monsters who should be kept away from normal
society. What modern woman is forgetting is her place. Women must be reminded that without rape we never would of moved past living
in caves and worshiping fire gods. Many of these methods still work today. While it may seem somewhat cartoonish, the club
to the head method can help subdue a woman who has not yet come to appreciate being raped. The woman, in a fit of rage producded
from attending feminist meetings or being allowed to read, may try to resist the rape by kicking clawing and scratching. This
can be avoided with a firm, yet loving strike to the head with a blunt object. If you see skull or brains you may of hit too hard.


        In this chapter I have established what a Rapelationship is, and how you can go about building your own sucessfull one.
Remember that making the first move is often the hardest, it may not be in your nature to rape, but you can bring yourself to it
if you too want a long loving rapelationship.

