\section*{Feminism and the World}

In recent times, the practice of Natural Coitus has come under scrutiny from both the powers that be, and a plethora 
of overzealous individuals who wish it torn asunder simply because it does not mesh with their solipsistic and outdated 
view of morality. This has happened partly because of how Natural Coitus comes across to may people, especially females 
and radical groups such as feminism. Feminism has sunk its jagged claws deep into the very fabric of our society, and, 
as such, commands a large amount of power and influence, especially among the female population and in politics.

Another reason for this rather expected turn of events is because the society of today has become increasingly 
liberal to the point of caricature. The old ways and time-honored traditions of Natural Coitus have becomes 
lost in a maelstrom of degenerate behavior as convervative attitudes have been swept away through decades 
of gradual erosion. The caustic and unnatural worldview that many women hold today directly correlates 
to the rise of feminism, which is itself the bastard child of Cultural Marxism. Both have contributed 
heavily to the infamy and societal persecution of those whose only wish is to practice the natural 
acts of coitus as was the norm in the not-so-distant past of their forefathers.

To illuminate and broaden our understaning of the subject, it must be mentioned that Feminist groups originally 
sprung from the Suffragette movement of the mid to late 1800s, with delusional women from all over Great Britain 
rising up against the superior males of the time. Committing ludicrous acts such as chaining themselves to lamp 
posts (and being general nuisances in order to get their way, much like a child would to persuade their much 
wiser parents to buy them a toy they will soon forget about, and will then move on to wanting something else), 
the women gradually wore down opposition to their cause, and destroyed their detractors piecemeal. The men 
of the time, although well-versed in politics and the social sciences, had little idea of what they were 
up against or the kind of monster it would metamorposize into.

Like tantrum-throwing children, the women marched and demanded their rights, and, in stark contrast to the 
rhetoric of oppression they so actively preach these days, were given everything they demanded. Rights that 
should not have been theirs were granted, concessions made, time-honored traditions trampled, and new laws 
enacted, forcing the carefree male to enfeeble and socially castrate himself in order to fulfill his most 
basic desire for sex (unless said male wished to be jailed for the newly-perpetrated transgressions).

And that indeed is what has happened over the years, with the radical-like feminists standing in the way of 
the processes deemed natural by most experts in gender studies, including myself, along with other professionals 
of similar standing. Natural Coitus is, by itself, simply the process of bringing into the world the next generation 
of great men. It is a natural act, and the stigma associated with it is, from a historal point of view, a recent thing. 
What was natural and widelay accepted only a hundred years ago has now been (to the detriment of us all) relegated to 
the realm of psychopathy.

Today, the Feminist movement is acting much like their Suffragette foremothers - in an extremely aggressive 
manner not befitting the valued, submissive woman. However, despite its long string of victories over the 
course of decades, it is clear the movement has actually lost momentum in recent years. Modern females 
may profess to it when among friends, and even live by its teachings, but, subconsciously, they crave 
the brutal, unyielding dominance of a superior male.

As the old proverb goes, a woman unchained is no woman at all!

The blind solipsism and rabid misandry infecting the Feminists of today keeps them sequestered in a bubble 
of their own making, effectively barring them from realizing these self-evident truths. Women in the 1800s 
were ruled over by men, but they wanted this leadership, *craved* it, for supplication and submission to 
women is what war and natural coitus are to men. It was only when the Suffragettes came along and blinded 
the logical thinking of perfectly well-behaved females that they suddenly came to the radical and silly 
ideas they hold today, namely to involve themselves in things that only men understand and have made 
their spheres of influence since time immemorial. 

Education, finance, politics, law enforcement... all bowed down and opened their doors to the fairer sex, 
admitting women into the chambers of hallowed institutions which had been male-oriented since their inception. 
Even the militaries of the developed world -- those ancient work horses of the nations which had defended their 
people through countless wars -- have, in many countries, allowed females within their ranks.

Nowadays, the Feminist have run out of false oppressions to rail against and equalities to demand, and so 
they dedicate their time and energies to denouncing and shaming those who would otherwise practice the most 
natural of processes, that which has, since the Neanderthals, demonstrated who among a tribe was true Alpha.

First, let us define that word, as done so by Merriam-Webster:
\begin{quote}
 al•pha ('æl fe)
\\
 n., pl. -phas,\\
 adj. n.
\begin{enumerate}
       \item the first letter of the Greek alphabet (A, a).
       \item the first; beginning.
       \item (cap.) the brightest star in a constellation: Alpha Centauri.
       \item the first or foremost in a series of related items. 
\end{enumerate}
 adj.
\begin{enumerate}
\setcounter{enumi}{4}
       \item \begin{enumerate}
          \item  (esp. of animals) having the highest rank of its sex in a dominance hierarchy: the alpha female.
          \item  being the most prominent, talented, or aggressive person in a group: the alpha male of investment bankers.
       \end{enumerate}
       \item pertaining or linked to the carbon atom closest to a particular group in an organic molecule. 
\end{enumerate}
\end{quote}

Now, it has been proven that females prefer the 'Alphas' of society. Ask any Female in the street, and more than 
ninety percent of them will say they prefer a confident, attractive, successful, and well-hung man. This is the most 
widely accept definition of the characteristics which, when they converge in one individual, make him an Alpha male.
Therefore, it is glaringly obvious that women are actually inviting Alphas to plant seeds inside their fertile wombs 
in an effort to secure for themselves and their future progeny the best possible DNA. After all, women are hypergamous, 
and it is socially acceptable (and encouraged) for them to seek the best possible mate, even if they themselves do not 
clome to scratching the upper echelons of female beauty (which is, in all honesty, the only metric of female value).

Returning to our earlier point, the only way of proving who is Alpha is the process of Natural Coitus, for only the 
daring, strong, accomplished, and fearless man posesses the ingenuity and strength of character to attempt Natural 
Coitus at a time of history when all outside variables are pitted against him. In a time when automated labor and 
mechanized warfare have all but replaced the male in fields which had been his proving grounds for untold eons, 
one of the only ways (maybe even the *only* way!) a modern man can demonstrate his value to a female is to rape her. 
This enforces his dominance upon her, and visibly demonstrates his ability to subdue both her mind and her body to 
his will, and at great peril to himself! For, he chances life imprisonment if caught, and the inability to leverage 
his victory over the current female in future conquests even if he succeeds in performing natural coitus without 
sufferring apprehension at the hands of the authorities.

In essence, what once was accepted and even celebrated is now shamed and maligned.

To finally weave all these threads together and put the whole picture into perspective, we must understand one 
final part of the puzzle, and that is the undeniable fact that most females *desire* rape, even if subconsciously. 
However, the majority of disenfranchised males today see feminism as a plague which has robbed them of their God-given
right to practice natural coitus. This, then, leads them to conclusion that feminists, in their fight against Natural 
Coitus, are therefore stopping the human race from progressing, and, as such, should be removed or used for males to 
practice Natural Coitus on. However, while the latter is true, that former is not entirely correct...

Those of us who study female behavior with a critical eye have come to understand that Feminism evolved out of a 
desire to test males. As already mentioned, there are few natural testing grounds left for a man living in the 
relative safety and comfort of the modern world, and the acquisition of wealth, while valuable to a female, does 
nothing to raise a man's status in her eyes if he is not posessed of physical stature, mental power, and dominance. 
And so, Feminism sprung into being, spawned in the darkest recesses of the female mind and nurtured from the 
percolating brine found therein to mature into its final and current form - that which we witness today.

Its *true* purpose is to enforce a life of celibacy for the majority of helpless Beta males, while taunting and 
goading the most capable and ruthless Alphas to defy the law (and common sense) in order to fulfill their need 
for natural coitus. In a way, Feminism is the ultimate mating strategy, as it ensures a win-win scenario for women 
by eliminating the worthless individuals (via proxy, as their own shortocmings consign them to a life of labor and 
self-imposed celibacy) while pushing the worthile to excellence.

It can be said that Feminism is a brilliant, infinitely complex and self-deluding apparatus the female mind has 
enacted in order to receive the rape they crave but eliminate the accompanying shame they do not desire.

Thus, Feminism serves as a mechanism which ennables natural coitus of the highest caliber.

In its purest form, feminism is the vehicle of rape.
